---
title: "Homework1"
output: html_notebook
---

```{r}
library("quantmod")
require("quantmod")
```

```{r}
sp500 <- new.env()
getSymbols("^GSPC", env = sp500, src = "yahoo", from = as.Date("1960-01-04"), to = as.Date("2009-01-01"))
GSPC <- sp500$GSPC
```

```{r}
SP500 <-read.csv("SP500constituentsSecid2016sector.csv", stringsAsFactors = FALSE, strip.white = TRUE)
SP500['Ticker']
```

```{r}
SP500 <- read.csv("SP500constituentsSecid2016sector.csv", header=TRUE, sep=",")
sp<- new.env()
for(i in SP500$Ticker){
#for (i in SP500['Ticker']){
  print(i)
  cat("Downloading time series for symbol '", i, "' ...\n", sep = "")
  status <- tryCatch(getSymbols(i, env = sp, src = "yahoo", from = as.Date("2007-01-01")), error = identity)
  if(inherits(status, "error")) cat("Symbol '", i, "' not downloadable!\n", sep = "")
}
```

```{r}
with(sp, AAPL)
```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.